New Exact Algorithms for Planar Maximum Covering Location by Ellipses Problems\tnoteref{t1}

### 2020-08-15 paper/answer_rev_2.tex
wip

		\textbf{Comment \#1:} ``The highlights (contributions of the paper) and organization of the remaining sections should be presented at the end of Section 1."

@@

		``This paper is organized as follows. Section 2 presents the definitions of both problems and
		3introduces some notations used throughout the rest of the work. An algorithm for MCE is developed
		in Section 3, and an algorithm for MCER in Section 5 with the observation that its development
		depends on a subproblem whose algorithm is developed in Section 4. Improvements suggestions to
		the implementations are given in Section 6 while the implementation details are given in Section 7.
		Numerical results are presented and analyzed in Section 8. Finally, a conclusion is given in Section 9."

@@

		\textbf{Comment \#2:} ``In my opinion `fixed shape' ellipses should be replaced by `fixed shape parameters' ellipses, or ellipses with the given semi-major and semi-minor axes. Alternately the term `fixed shape' ellipses should be explained."

		Thanks for the great observation; we agree that it is not very clear what the term 'fixed shape' ellipses means, and decided to rewrite the text everywhere it appeared. Please find below the changes we have made:
		\begin{itemize}
			\item In the first paragraph of the abstract (page 2), we used the term ``given their major and minor axis" to better convey the same idea.

@@

		Thanks for the comment, we addressed this issued by adding a new paragraph to our Introduction citing the work ``\textit{Mustafa S. Canbolat and Michael von Massow. Planar maximal covering with ellipses.}", which covers with great detail the practical applications of the problems studied in our work:

@@

		'A Combinatorial Maximum Cover Approach to 2D Translational Geometric Covering' by K. Daniels A. Mathur R. Grinde

		'Covering a polygonal region by rectangles' by G. Scheithauer, Y. Stoyan, T. Romanova, A. Krivulya

		'Translational polygon containment and minimal enclosure' using mathematical programming
		by V.J. Milenkovic , K. Daniels

		and references in 2007 PhD thesis of Daoqin Tong from the Ohio State University."

		Thanks for all the great suggestions, after pondering about it, we agree that our literature review needed work, thanks for pointing it out.
		We spent some time on trying to improve it, in summary, those are the changes we have made to our introduction:

@@

	We did consider the list of works you gave us as suggestions, however, even though we think they are great papers, we decided to cite two works we were more familiar with. It is worth mentioning though, that some works of Daoqin Tong are cited in the survey paper we are using.
\\

		\textbf{Comment \#5:} ``Please, clarify what is the critical parameter for your algorithm: the number of ellipses or the number of demand points?"

		We addressed this issue in section 8.2 ``New instances" (page 19):

@@

		\textbf{Comment \#6:} ``In the paper overlapping of covering ellipses is allowed, i.e. a demand point can be covered by more than one ellipse. However, it seems natural that the weight of the demand point covered by various ellipses can differ from the weight of the same point covered by only one ellipse."

@@

		\textbf{Comment \#7:} ``What happens if no overlapping between covering ellipses is allowed. Please, comment on this."

@@

		The solution shown is non-overlapping -- actually there are an infinite number of non-overlapping equivalent solutions --, however, our algorithm would fail to find any equivalent solution. Notice that moving the ellipse with no points on its coverage region's border in order to put at least two points on it would cause overlap.
		We believe methods for the problems with this additional constraint would have to come from a different basis.

>>>>

		\textbf{Comment \#1:} ``The highlights (contributions of the paper) and organization of the remaining sections should be presented at the end of Section 1."
		\\

@@

		``This paper is organized as follows. Section 2 presents the definitions of both problems and introduces some notations used throughout the rest of the work. An algorithm for MCE is developed
		in Section 3, and an algorithm for MCER in Section 5 with the observation that its development
		depends on a subproblem whose algorithm is developed in Section 4. Improvements suggestions to
		the implementations are given in Section 6 while the implementation details are given in Section 7.
		Numerical results are presented and analyzed in Section 8. Finally, a conclusion is given in Section 9."

@@

		\textbf{Comment \#2:} ``In my opinion `fixed shape' ellipses should be replaced by `fixed shape parameters' ellipses, or ellipses with the given semi-major and semi-minor axes. Alternately the term `fixed shape' ellipses should be explained."
		\\

		Thanks for the great observation; we agree that it is not very clear what the term `fixed shape' ellipses means, and decided to rewrite the text everywhere it appeared. Please find below the changes we have made:
		\begin{itemize}
			\item In the first paragraph of the abstract (page 2), we used the term ``given their major and minor axis" to better convey the same idea.

@@

		Thanks for the comment, we addressed this issued by adding a new paragraph to our Introduction citing the work ``\textit{Mustafa S. Canbolat and Michael von Massow. Planar maximal covering with ellipses.}", which covers with great detail the practical applications of the problems studied in our work:
		\\

@@

		`A Combinatorial Maximum Cover Approach to 2D Translational Geometric Covering' by K. Daniels A. Mathur R. Grinde

		`Covering a polygonal region by rectangles' by G. Scheithauer, Y. Stoyan, T. Romanova, A. Krivulya

		`Translational polygon containment and minimal enclosure' using mathematical programming
		by V.J. Milenkovic , K. Daniels

		and references in 2007 PhD thesis of Daoqin Tong from the Ohio State University."
		\\

		Thanks for all the great suggestions, after pondering about it, we agree that our literature review needed work, it is great that you pointed it out.
		We spent some time on trying to improve it, and in summary, those are the changes we have made to our Introduction:

@@

	We did consider the list of works you gave us as suggestions, however, even though we think they are great papers, we decided to cite works that we judged to be closer to the problems we are studying. We also had the goal to not extend the literature review too much, as the field of geometric covering is too vast, we tried to keep it concise by only citing works that study very specific problems, and a survey paper.
	It is worth mentioning though, that some works of Daoqin Tong are cited in the survey paper we are using. If after reading this, you still feel like our literature review is not satisfactory, we can change it to include your suggestions.
\\

		\textbf{Comment \#5:} ``Please, clarify what is the critical parameter for your algorithm: the number of ellipses or the number of demand points?"
		\\

		We addressed this issue in Section 8.2 ``New instances" (page 19):

@@

		\textbf{Comment \#6:} ``In the paper overlapping of covering ellipses is allowed, i.e. a demand point can be covered by more than one ellipse. However, it seems natural that the weight of the demand point covered by various ellipses can differ from the weight of the same point covered by only one ellipse."
		\\

@@

		\textbf{Comment \#7:} ``What happens if no overlapping between covering ellipses is allowed. Please, comment on this."
		\\

@@

		The solution shown is non-overlapping -- actually there are an infinite number of non-overlapping equivalent solutions --. However, our algorithm would fail to find any equivalent solution. Notice that moving the ellipse with no points on its coverage region's border in order to put at least two points on it would cause overlap.
		We believe methods for the problems with this additional constraint would have to come from a different basis.

### 2020-08-15 paper/comments_to_reviewers.tex
wip

			\begin{itemize}
				\item The {\color{Red} red} highlights are corrections concerning the points made by reviwer \#1.

				\item The {\color{Green} green} highlights are corrections concerning the points made by reviwer \#2.

>>>>

			\begin{itemize}
				\item The {\color{Red} red} highlights are corrections concerning the points made by reviewer \#1.

				\item The {\color{Green} green} highlights are corrections concerning the points made by reviewer \#2.
